Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-01-15 lqg-strings.tex
Reverted accidental deletion (by me) of Luigi's section on quantization of string action.

In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov string. We start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
\begin{multline} \label{eqn:inverse-metric-Polyakov}
	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{multline}
The equations of motion for the world-sheet metric are completely unchanged by this correction, so they are
\begin{equation} \label{eqn:vary-wrt-g}
	\frac{\delta S_{I A P}}{\delta g^{c d}} \overset{!}{=} 0
\end{equation}
from which we obtain the stress-energy tensor for the worldsheet:
\begin{multline} \label{eqn:inverse-area-em-tensor}
	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0 ,
\end{multline}
from which we can extract the metric $g_{c d}$ as
\begin{equation} \label{eqn:ws-metric}
	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f$ is given by
\begin{equation} \label{eqn:inverse-area-f}
	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{equation}

@@

As usual, by the appearance of the Minkowski metric in the non-zero commutator
\begin{equation} \label{eqn:ghosts}
	\Big[ \Hat{a}^{\mu} _{p} , (\Hat{a}^{\nu} _{k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p k} ,
\end{equation}
we have ghosts in the theory which must be dealt with. When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
\begin{equation} \label{eqn:L-constraint-quantum-1}
	\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
\end{equation}
\begin{equation} \label{eqn:L-constraint-quantum-2}
	\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
\end{equation}
$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators, however, we have an ambiguity for $\Hat{\widetilde{L}}_{p , 0}$. To resolve this issue, we pick
\begin{equation} \label{eqn:L-normal-ordering}
	\Hat{\widetilde{L}}_{p , 0} = \frac{- p}{E_{- p}} (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu}
\end{equation}
with the annihilation operator to the right, which manifests in the imposition of the constraint as
\begin{equation} \label{eqn:shifted-L-constraint}
	\bra{\phi} \Hat{\widetilde{L}}_{p , 0} - c_{p} \ket{\psi} = 0 ,
\end{equation}
for some sequence $c_{p}$. The reason for it to be a sequence of $p$ and not a constant like in the regular String Theory literature is that in the usual theory, we would have a sum over $p$ and thus it would end up being a constant, but in our analysis we have this extra freedom, which we'll now see ends up being important. Classically, we had eq(\ref{eqn:string-rest-mass}) for the string rest mass, which we can rewrite as
\begin{equation} \label{eqn:alternative-classical-rest-mass}
	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{p \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
\end{equation}
from where we can now see that the string mass spectrum will get shifted by
\begin{equation} \label{eqn:shifted-mass-spectrum}
	\Hat{M}^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \left( (\Hat{\alpha} ^{\mu} _{0})^{\dagger} \Hat{\alpha}^{\nu} _{0} \eta _{\mu \nu} + \lim _{p \rightarrow 0} \frac{E_{p}}{p} c_{p} \right) .
\end{equation}
Since $E_{0} = \mu$, it seems like the natural candidate for $c_{p}$ would be some function $f (\mu , p)$ such that
\begin{equation} \label{eqn:cp-limit}
	\lim _{p \rightarrow 0} \frac{c_{p}}{p} = \mu
\end{equation}
like $c_{p} = \mu p$, $c_{p} = \sin (\mu p)$, $c_{p} = \tan (\mu p)$, etc, making it so the mass spectrum of the string gets shifted by the \textquotedblleft mass" term of the Klein-Gordon equation (\ref{eqn:X-Klein-Gordon-eqn}), $\mu ^2$.

@@

\section{The Bimetric String}\label{sec:bimetric-nambu-goto}

@@

\section{Strings and Quantum Geometry}\label{sec:string-geometry}

Let us begin by writing down the action of a string propagating in a background geometry which is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$. Further, we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\omega _{a} ^{i j}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$. In order for the bulk connection $A_\mu^{IJ}$, and its pullback $\omega _a ^{i j}$ on $\Sigma$, to have an effect on the string dynamics we will also promote the embedding fields $X^\mu$ to Lie algebra valued vector fields $X^{\mu} _{I}$. However, due to the fact that parallel transport of the embedding fields on the worldsheet should only involve the worldsheet connection $\omega _a ^{i j}$, we can replace $X^{\mu} _{I}$ with $X^{\mu} _{i}$, and to not lose the physical meaning of embedding fields as string coordinates, we include a new internal world-sheet field $v^{i}$, and define the string coordinates to be $\Tilde{X}^{\mu} \equiv X^{\mu} _{i} v^{i}$.
\begin{multline} \label{eqn:lqg-string-action}
	S_{PA} = - \frac{T}{2} \int \diff \tau \wedge \diff \sigma e e^{a} _{i} e^{b i} D_{a} X^{\mu} _{j} v^{j} \times \\
	\times D_{b} X^{\nu} _{k} v^{k} E_{\mu} ^{I} E_{\nu I} ,
\end{multline}
where $e = \det (e^{i} _{a})$ and $D_a$ is the covariant derivative with respect to the worldsheet connection, and is given by:
\begin{equation} \label{eqn:worldsheet-deriv}
	D_a X^{\mu} _{i} = \partial_a X^{\mu} _{i} - \omega_{a\,i}^{j} X^{\mu} _{j} ,
\end{equation}
where $\omega_{a\,j}^i$ is the pullback of the bulk connection to the worldsheet.

\section{Physical Implications}

\section{Discussion}

\begin{acknowledgments}

\end{acknowledgments}

\appendix

\section{}

>>>>

In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov string. we start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
\begin{multline} \label{eqn:inverse-metric-Polyakov}
	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{multline}
The equations of motion for the world-sheet metric are completely unchanged by this correction, so they are
\begin{equation} \label{eqn:vary-wrt-g}
	\frac{\delta S_{I A P}}{\delta g^{c d}} \overset{!}{=} 0
\end{equation}
from which we obtain the stress-energy tensor for the worldsheet:
\begin{multline} \label{eqn:inverse-area-em-tensor}
	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0 ,
\end{multline}
from which we can extract the metric $g_{c d}$ as
\begin{equation} \label{eqn:ws-metric}
	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f$ is given by
\begin{equation} \label{eqn:inverse-area-f}
	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{equation}

@@

As usual, by the appearance of the Minkowski metric in the non-zero commutator
\begin{equation} \label{eqn:ghosts}
	\Big[ \Hat{a}^{\mu} _{p} , (\Hat{a}^{\nu} _{k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p k} ,
\end{equation}
we have ghosts in the theory which must be dealt with. When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
\begin{equation} \label{eqn:L-constraint-quantum-1}
	\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
\end{equation}
\begin{equation} \label{eqn:L-constraint-quantum-2}
	\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
\end{equation}
$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators, however, we have an ambiguity for $\Hat{\widetilde{L}}_{p , 0}$. To resolve this issue, we pick
\begin{equation} \label{eqn:L-normal-ordering}
	\Hat{\widetilde{L}}_{p , 0} = \frac{- p}{E_{- p}} (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu}
\end{equation}
with the annihilation operator to the right, which manifests in the imposition of the constraint as
\begin{equation} \label{eqn:shifted-L-constraint}
	\bra{\phi} \Hat{\widetilde{L}}_{p , 0} - c_{p} \ket{\psi} = 0 ,
\end{equation}
for some sequence $c_{p}$. The reason for it to be a sequence of $p$ and not a constant like in the regular String Theory literature is that in the usual theory, we would have a sum over $p$ and thus it would end up being a constant, but in our analysis we have this extra freedom, which we'll now see ends up being important. Classically, we had eq(\ref{eqn:string-rest-mass}) for the string rest mass, which we can rewrite as
\begin{equation} \label{eqn:alternative-classical-rest-mass}
	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{n \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
\end{equation}
from where we can now see that the string mass spectrum will get shifted by
\begin{equation} \label{eqn:shifted-mass-spectrum}
	\Hat{M}^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \left( (\Hat{\alpha} ^{\mu} _{0})^{\dagger} \Hat{\alpha}^{\nu} _{0} \eta _{\mu \nu} + \lim _{p \rightarrow 0} \frac{E_{p}}{p} c_{p} \right) .
\end{equation}
Since $E_{0} = \mu$, it seems like the natural candidate for $c_{p}$ would be some function $f (\mu , p)$ such that
\begin{equation} \label{eqn:cp-limit}
	\lim _{p \rightarrow 0} \frac{c_{p}}{p} = \mu
\end{equation}
like $c_{p} = \mu p$, $c_{p} = \sin (\mu p)$, $c_{p} = \tan (\mu p)$, etc, making it so the mass spectrum of the string gets shifted by the \textquotedblleft mass" term of the Klein-Gordon equation (\ref{eqn:X-Klein-Gordon-eqn}), $\mu ^2$.

@@

\section{The Bimetric String}\label{app:bimetric-string}

@@
